Effects of Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates on Sheath Blight of Rice

### 2020-08-11 analysis/paper/paper.Rmd
Delete "normally"

It should be noted that the levels of leaf severity remained low (<&nbsp;1\%) throughout the growing season in all treatments for both years.
Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
However, it should be noted that normally it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.

>>>>

It should be noted that the levels of leaf severity remained low (<&nbsp;1\%) throughout the growing season in all treatments for both years.
Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
However, it should be noted that it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.
